On the Limitations of Weighted Model Counting

### 2020-03-27 paper.tex
A few proven and/or stated lemmas

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{conjecture}{Conjecture}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}

@@

%\title{On the Limitations of Weighted Model Counting}
\title{Weighted Model Counting/Integration from the Perspective of Boolean Algebras}
%\title{What Boolean Algebras Can Teach Us About Weighted Model Counting/Integration?}
\author{Paulius Dilkas}

@@

Previous/related work:
\begin{itemize}
\item Hailperin's approach to probability logic
  \cite{DBLP:journals/ndjfl/Hailperin84}
\item Nilsson's (somewhat successful) probabilistic logic
  \cite{DBLP:journals/ai/Nilsson86}
\item Semiring programming \cite{DBLP:journals/corr/BelleR16}
\item WMI \cite{DBLP:conf/ijcai/BellePB15}
\item Measures on Boolean algebras: overview articles (from most cited to least
  cited)
  \begin{itemize}
  \item Horn and Tarski \cite{horn1948measures}
  \item Concerning measures on Boolean algebras \cite{gaifman1964concerning}
  \item Jech -- Measures on Boolean algebras (arXiv) \cite{jech2017measures}
  \end{itemize}
\item Measures on Boolean algebras: more specific articles
  \begin{itemize}
  \item On possibility and probability measures in finite Boolean algebras
    \cite{DBLP:journals/soco/CastineiraCT02}
  \item Representation of conditional probability measures
    \cite{krauss1968representation}
  \end{itemize}
\end{itemize}

@@

\begin{definition}[\cite{DBLP:books/daglib/0090259,levasseur2012applied}]
  An element $a \ne 0$ of $\mathbf{B}$ is an \emph{atom} if, for all $x \in
  \mathbf{B}$, either $x \land a = a$ or $x \land a = 0$. Equivalently, $a \ne
  0$ is an atom if there is no $x \in \mathbf{B}$ such that $0 < x < a$. The BA
  $\mathbf{B}$ is \emph{atomic} if for every $a \in \mathbf{B} \setminus \{0
  \}$, there is an atom $x$ such that $x \le a$.
\end{definition}

@@

\begin{definition}[\cite{gaifman1964concerning,DBLP:books/daglib/0090259}] \label{def:measure}
  A \emph{measure} on $\mathbf{B}$ is a function $m\colon
  \mathbf{B} \to \mathbb{R}_{\ge 0}$ such that:
  \begin{itemize}
  \item $m(0) = 0$;
  \item $m(x \lor y) = m(x) + m(y)$ for all $x, y \in \mathbf{B}$ whenever $x
    \land y = 0$.
  \end{itemize}
  If $m(1) = 1$, we call $m$ a \emph{probability measure}. Also, if $m(x) > 0$
  for all $x \ne 0$, then $m$ is \emph{strictly positive}.
\end{definition}

@@

\begin{definition}[\cite{givant2008introduction}]
  Let $I$ be an ideal in $\mathbf{B}$. The \emph{quotient algebra of
    $\mathbf{B}$ modulo the ideal $I$} $\mathbf{B}/I$ is a BA
  of equivalence classes of elements of $\mathbf{B}$ with respect to the
  equivalence relation
  \[
    a \sim b \quad \iff \quad a + b \in I
  \]
  for all $a, b \in \mathbf{B}$. Elements of $\mathbf{B}/I$ are usually denoted
  by $a/I$ (for some $a \in \mathbf{B}$) with the understanding that if $b \sim
  a$ (for some $b \in \mathbf{B}$), then $b/I = a/I$. The three algebraic
  operations on $\mathbf{B}/I$ are defined as
  \begin{align*}
    a/I \land b/I &= a \land b / I, \\
    a/I \lor b/I &= a \lor b / I, \\
    \neg(a/I) &= (\neg a)/I.
  \end{align*}
\end{definition}

@@

\begin{definition} \label{def:wmc}
  Let $\mathbf{B}$ be an atomic BA, and let $M \subset \mathbf{B}$ be its set of
  atoms. Let $L \subset \mathbf{B}$ be such that every atom $m \in M$ can be
  uniquely expressed as $m = \bigwedge L'$ for some $L' \subseteq L$, and let
  $w\colon L \to \mathbb{R}_{\ge 0}$ be arbitrary. The \emph{weighted model
    count} $\WMC_w\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ is defined as
  \[
    \WMC_w(x) = \begin{cases}
      0 & \text{if } x = 0 \\
      \prod_{l \in L'} w(l) & \text{if } M \ni x = \bigwedge L' \\
      \sum_{\text{atoms } a \le x} \WMC_w(a) & \text{otherwise}
    \end{cases}
  \]
  for any $x \in \mathbf{B}$. Furthermore, we define the \emph{normalised
    weighted model count} $\nWMC_w\colon \mathbf{B} \to [0, 1]$ as $\nWMC_w(x) =
  \frac{\WMC_w(x)}{\WMC_w(1)}$ for all $x \in \mathbf{B}$. For both $\WMC_w$ and
  $\nWMC_w$, we will drop the subscript when doing so results in no potential
  confusion.
\end{definition}

@@

\begin{lemma}
  For any measure $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ and elements $a, b
  \in \mathbf{B}$,
  \[
    m(a \lor b) = m(a) + m(b) - m(a \land b).
  \]
\end{lemma}
\begin{proof}
  By \cref{def:measure},
  \begin{align*}
    m(a) &= m(a \land b) + m(a \land \neg b), \\
    m(b) &= m(a \land b) + m(\neg a \land b), \\
    m(a \lor b) &= m(a \land b) + m(a \land \neg b) + m(\neg a \land b),
  \end{align*}
  so
  \[
    m(a) + m(b) - m(a \land b) = m(a \land b) + m(a \land \neg b) + m(\neg a
    \land b) = m(a \lor b)
  \]
  as required.
\end{proof}

\begin{lemma} \label{lemma:well-defined}
  For any $a, b \in \mathbf{B}$ and any principal ideal $(p)$, if $a/(p) =
  b/(p)$, then $a \lor p = b \lor p$.
\end{lemma}
\begin{proof} % TODO: update
  If $a/F = b/F$, then $a \to b \in F$ by \cref{def:quotient}. Then $p \le a \to
  b$ by \cref{def:filter}, and $(a \to b) \land p = p$ by the definition of
  $\le$. Then
  \[
    1 = p \lor \neg p = ((a \to b) \lor \neg p) \land (p \lor \neg p) = \neg a
    \lor b \lor \neg p = \neg (a \land p) \lor b.
  \]
  So
  \[
    \neg b = (\neg(a \land p) \land \neg b) \lor (b \land \neg b) = \neg((a
    \land p) \lor b),
  \]
  and thus $b = (a \land p) \lor b$, and
  \[
    b \land p = (a \land p) \lor (b \land p) = (a \lor b) \land p.
  \]
  Similarly, $a \land p = (a \lor b) \land p$ which proves that $a \land p = b
  \land p$.
\end{proof}

\begin{proposition}[Measures on quotients] \label{def:measures_on_quotients}
  Let $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ be a measure, and let $(p)$ be
  a principal ideal. Let $m^*\colon \mathbf{B}/(p) \to \mathbb{R}_{\ge 0}$ be
  defined as
  \[
    m^*(a/(p)) = m(a \lor p)
  \]
  for any $a \in \mathbf{B}$. The function $m^*$ is well-defined. Furthermore,
  it is a measure on $\mathbf{B}/(p)$ if and only if $m(p) = 0$. Moreover, if it
  is a measure, then the following properties transfer from $m$ to $m^*$:
  \begin{itemize}
  \item if $m$ is a probability measure, then so is $m^*$;
  \item if $m$ is strictly positive, then so is $m^*$;
  \item if $m$ is a WMC measure, then so is $m^*$.
  \end{itemize}
\end{proposition}
\begin{proof} % TODO: prove this
  \Cref{lemma:well-defined} proves that the function is well-defined.
\end{proof}

% TODO: prove that the two ways to compute the probability give the same answer.

>>>>

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}

@@

\title{On the Limitations of Weighted Model Counting}
%\title{Weighted Model Counting/Integration from the Perspective of Boolean Algebras}
%\title{What Boolean Algebras Can Teach Us About Weighted Model Counting/Integration?}
\author{Paulius Dilkas}

@@

Previous/related work:
\begin{itemize}
\item Hailperin's approach to probability logic
  \cite{DBLP:journals/ndjfl/Hailperin84}
\item Nilsson's (somewhat successful) probabilistic logic
  \cite{DBLP:journals/ai/Nilsson86}
\item Logical induction: a huge paper with a good overview of previous attempts
  to assign probabilities to logical sentences in a way that makes sense
  \cite{DBLP:journals/eccc/GarrabrantBCST16}.
\item Semiring programming \cite{DBLP:journals/corr/BelleR16}
\item WMI \cite{DBLP:conf/ijcai/BellePB15}
\item Measures on Boolean algebras: more specific articles
  \begin{itemize}
  \item On possibility and probability measures in finite Boolean algebras
    \cite{DBLP:journals/soco/CastineiraCT02}
  \item Representation of conditional probability measures
    \cite{krauss1968representation}
  \end{itemize}
\end{itemize}

@@

\begin{definition}[\cite{DBLP:books/daglib/0090259,levasseur2012applied}]
  An element $a \ne 0$ of $\mathbf{B}$ is an \emph{atom} if, for all $x \in
  \mathbf{B}$, either $x \land a = a$ or $x \land a = 0$. Equivalently, $a \ne
  0$ is an atom if there is no $x \in \mathbf{B}$ such that $0 < x < a$. We say
  that $\mathbf{B}$ is \emph{atomic} if for every $a \in \mathbf{B} \setminus \{0
  \}$, there is an atom $x$ such that $x \le a$.
\end{definition}

@@

\begin{definition}[\cite{gaifman1964concerning,DBLP:books/daglib/0090259}] \label{def:measure}
  A \emph{measure} on $\mathbf{B}$ is a function $m\colon
  \mathbf{B} \to \mathbb{R}_{\ge 0}$ such that:
  \begin{itemize}
  \item $m(0) = 0$;
  \item $m(a \lor b) = m(a) + m(b)$ for all $a, b \in \mathbf{B}$ whenever $a
    \land b = 0$.
  \end{itemize}
  If $m(1) = 1$, we call $m$ a \emph{probability measure}. Also, if $m(x) > 0$
  for all $x \ne 0$, then $m$ is \emph{strictly positive}.
\end{definition}

\begin{lemma}[\cite{horn1948measures}] \label{lemma:m_and_order}
  Let $m: \mathbf{B} \to \mathbb{R}_{\ge 0}$ be a measure. For any $a, b \in
  \mathbf{B}$, if $a \le b$, then $m(a) \le m(b)$.
\end{lemma}

@@

\begin{definition}[\cite{givant2008introduction}] \label{def:quotient}
  Let $I$ be an ideal in $\mathbf{B}$. The \emph{quotient algebra of
    $\mathbf{B}$ modulo the ideal $I$} $\mathbf{B}/I$ is a BA
  of equivalence classes of elements of $\mathbf{B}$ with respect to the
  equivalence relation
  \[
    a \sim b \quad \iff \quad a + b \in I
  \]
  for all $a, b \in \mathbf{B}$. Elements of $\mathbf{B}/I$ are usually denoted
  by $a/I$ (for some $a \in \mathbf{B}$) with the understanding that if $b \sim
  a$ (for some $b \in \mathbf{B}$), then $b/I = a/I$. The three algebraic
  operations on $\mathbf{B}/I$ are defined as
  \begin{align*}
    a/I \land b/I &= a \land b / I, \\
    a/I \lor b/I &= a \lor b / I, \\
    \neg(a/I) &= (\neg a)/I.
  \end{align*}
\end{definition}

\begin{definition}[\cite{givant2008introduction}]
  Let $\mathbf{A}$ and $\mathbf{B}$ be BAs. A \emph{(Boolean) homomorphism} from
  $\mathbf{A}$ to $\mathbf{B}$ is a map $f\colon \mathbf{A} \to \mathbf{B}$ such
  that:
  \begin{itemize}
  \item $f(x \land y) = f(x) \land f(y)$,
  \item $f(x \lor y) = f(x) \lor f(y)$,
  \item $f(\neg x) = \neg f(x)$
  \end{itemize}
  for all $x, y \in \mathbf{A}$.
\end{definition}

\begin{lemma}[\cite{givant2008introduction}] \label{lemma:canonical_homomorphism}
  Let $I \subseteq \mathbf{B}$ be an ideal. The map $f\colon \mathbf{B} \to
  \mathbf{B}/I$ defined by $f(x) = x/I$ is a homomorphism.
\end{lemma}

\begin{lemma}[Homomorphisms preserve order
  \cite{givant2008introduction}] \label{lemma:homomorphisms_and_order}
  Let $f\colon \mathbf{A} \to \mathbf{B}$ be a homomorphism between two BAs
  $\mathbf{A}$ and $\mathbf{B}$. Then, for any $x, y \in \mathbf{A}$, if $x \le
  y$, then $f(x) \le f(y)$.
\end{lemma}

\begin{lemma}[\cite{sikorski1969boolean}] \label{lemma:order}
  For any $a, b \in \mathbf{B}$, $a \le b$ if and only if $a \land \neg b = 0$.
\end{lemma}

% TODO: make up my mind about a,b vs x,y and stick to it (maybe x,y?)
% TODO: perhaps reorder things into paragraphs, i.e., a paragraph for order, for
% homomorphisms, for ideals and quotients. This would take up less space.

@@

\begin{definition} \label{def:wmc}
  Let $\mathbf{B}$ be an atomic BA, and let $M \subset \mathbf{B}$ be its set of
  atoms. Let $L \subset \mathbf{B}$ be such that every atom $m \in M$ can be
  uniquely expressed as $m = \bigwedge L'$ for some $L' \subseteq L$, and let
  $w\colon L \to \mathbb{R}_{\ge 0}$ be arbitrary. The \emph{weighted model
    count} $\WMC_w\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ is defined as
  \[
    \WMC_w(x) = \begin{cases}
      0 & \text{if } x = 0 \\
      \prod_{l \in L'} w(l) & \text{if } M \ni x = \bigwedge L' \\
      \sum_{\text{atoms } a \le x} \WMC_w(a) & \text{otherwise}
    \end{cases}
  \]
  for any $x \in \mathbf{B}$. Furthermore, we define the \emph{normalised
    weighted model count} $\nWMC_w\colon \mathbf{B} \to [0, 1]$ as $\nWMC_w(x) =
  \frac{\WMC_w(x)}{\WMC_w(1)}$ for all $x \in \mathbf{B}$. For both $\WMC_w$ and
  $\nWMC_w$, we will drop the subscript when doing so results in no potential
  confusion.
%  Finally, we say that a measure $m\colon \mathbf{B} \to
%  \mathbb{R}_{\ge 0}$ is a \emph{WMC measure} (or is \emph{WMC-computable}) if
%  there exists a subset $L \subset \mathbf{B}$ and a weight function $w\colon L
%  \to \mathbb{R}_{\ge 0}$ such that $m = \WMC_w$.
\end{definition}
% TODO: mention that the definition can be reduced to a single formula (i.e.,
% without cases)
% TODO: any measure is a WMC measure if all atoms are in L

@@

\begin{lemma} \label{lemma:sum}
  For any measure $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ and elements $a, b
  \in \mathbf{B}$,
  \[
    m(a \lor b) = m(a) + m(b) - m(a \land b).
  \]
\end{lemma}
\begin{proof}
  By \cref{def:measure},
  \begin{align*}
    m(a) &= m(a \land b) + m(a \land \neg b), \\
    m(b) &= m(a \land b) + m(\neg a \land b), \\
    m(a \lor b) &= m(a \land b) + m(a \land \neg b) + m(\neg a \land b),
  \end{align*}
  so
  \[
    m(a) + m(b) - m(a \land b) = m(a \land b) + m(a \land \neg b) + m(\neg a
    \land b) = m(a \lor b)
  \]
  as required.
\end{proof}

\begin{lemma} \label{lemma:well-defined}
  For any $a, b \in \mathbf{B}$ and any principal ideal $(p)$, if $a/(p) =
  b/(p)$, then $a \lor p = b \lor p$.
\end{lemma}
\begin{proof}
  Note that
  \[
    a/(p) = b/(p) \quad \iff \quad a+b \in (p) \quad \iff \quad a+b \le p \quad
    \iff \quad (a+b) \lor p = p
  \]
  by \cref{def:quotient,def:ideal}, and the definition of $\le$. So $p = (a
  \land \neg b) \lor (\neg a \land b) \lor p$, and thus
  \[
    0 = p \land \neg p = (a \land \neg b \land \neg p) \lor (\neg a \land b
    \land \neg p) \lor (p \land \neg p) = (a \land \neg (b \lor p)) \lor (b
    \land \neg (a \lor p)).
  \]
  It follows that
  \[
    a \land \neg (b \lor p) = 0 \quad \text{and} \quad b \land \neg (a \lor p) =
    0.
  \]
  Focusing on the first equation,
  \[
    \neg a = (\neg a \lor a) \land [\neg a \lor \neg (b \lor p)] = \neg [a \land
    (b \lor p)],
  \]
  and so $a = a \land (b \lor p)$, and
  \[
    a \lor p = (a \lor p) \land (b \lor p) = (a \land b) \lor p.
  \]
  By similar arguments, $b \lor p = (a \land b) \lor p$ as well which shows that
  $a \lor p = b \lor p$ as required.
\end{proof}

\begin{proposition}[Measures on quotients] \label{def:measures_on_quotients}
  Let $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ be a measure, and let $(p)$ be
  a principal ideal. Let $m^*\colon \mathbf{B}/(p) \to \mathbb{R}_{\ge 0}$ be
  defined as
  \[
    m^*(a/(p)) = m(a \lor p)
  \]
  for any $a \in \mathbf{B}$. The function $m^*$ is well-defined. Furthermore,
  it is a measure on $\mathbf{B}/(p)$ if and only if $m(p) = 0$. Moreover, if it
  is a measure, then the following properties transfer from $m$ to $m^*$:
  \begin{itemize}
  \item if $m$ is a \emph{probability measure}, then so is $m^*$;
  \item if $m$ is \emph{strictly positive}, then so is $m^*$.
  \end{itemize}
\end{proposition}
\begin{proof}
  \Cref{lemma:well-defined} proves that the function is well-defined. Next,
  note that
  \[
    m^*(0/(p)) = m(0 \lor p) = m(p),
  \]
  so $m^*(0/(p)) = 0$ if and only if $m(p) = 0$. For the second part of
  \cref{def:measure}, let $a/(p), b/(p) \in \mathbf{B}/(p)$ be such that
  \[
    a/(p) \land b/(p) = a \land b / (p) = 0 / (p).
  \]
  This condition is equivalent to $a \land b \in (p)$ and $(a \land b) \lor p =
  p$ by well-known properties of quotients and ideals
  \cite{givant2008introduction}, \cref{def:ideal}, and the definition of $\le$,
  respectively. Now
  \begin{align*}
    m^*(a/(p) \lor b/(p)) &= m^*(a \lor b / (p)) = m(a \lor b \lor p) = m((a \lor p) \lor (b \lor p)) \\
                          &= m(a \lor p) + m(b \lor p) - m((a \lor p) \land (b \lor p)) \\
                          &= m^*(a/(p)) + m^*(b/(p)) - m((a \lor p) \land (b \lor p))
  \end{align*}
  by \cref{lemma:sum}. However
  \[
    (a \lor p) \land (b \lor p) = (a \land b) \lor p = p,
  \]
  so $m^*(a/(p) \lor b/(p)) = m^*(a/(p)) + m^*(b/(p))$ if and only if $m(p) = 0$.

  The two remaining properties are easy to prove:
  \begin{itemize}
  \item If $m(1) = 1$, then $m^*(1/(p)) = m(1 \lor p) = m (1) = 1$.
  \item Suppose that $m$ is strictly positive, and let $a/(p) \in
    \mathbf{B}/(p)$ be such that $a/(p) \ne 0/(p)$. Then
    \[
      m^*(a/(p)) = m(a \lor p) \ge m(a) > 0,
    \]
    where the first inequality comes from an elementary property of $\le$ that
    $x \le x \lor y$ for any $x, y \in \mathbf{B}$ \cite{sikorski1969boolean}
    and \cref{lemma:m_and_order}; and the second inequality follows because
    $a/(p) \ne 0/(p)$ implies that $a \ne 0$, and $m$ is assumed to be strictly
    positive.
  \end{itemize}
\end{proof}
% TODO: add parentheses around quotients (e.g., (a+b)/I).
% TODO: I think I need to cite something for: a/I = 0/I <=> a \in I

\subsection{Lots of Lemmas}

% TODO: maybe 'unite' this with the result about a \/ p, i.e., a ~ a \/ p ~ a /\
% ~p.
% TODO: maybe I should state that A,B are assumed to be BAs with no additional
% properties unless stated otherwise.
\begin{lemma} \label{lemma:elements_in_quotients}
  Let $(p)$ be a principal ideal. Then for any $a \in \mathbf{B}$, $(a \land
  \neg p)/(p) = a/(p)$.
\end{lemma}
\begin{proof}
  Note that
  \[
    (a \land \neg p)/(p) = a/(p) \quad \iff \quad (a \land \neg p) + a \in (p)
    \quad \iff \quad (a \land \neg p) + a \le p.
  \]
  We also have that
  \[
    (a \land \neg p) + a = (a \land \neg p \land \neg a) \lor (\neg(a \land \neg
    p) \land a) = (\neg a \lor p) \land a = (\neg a \land a) \lor (p \land a) =
    p \land a.
  \]
  And, since $p \land a \le p$, we have that $(a \land \neg p) + a \le p$ as
  required.
\end{proof} % TODO: why? (the last bit) It's elementary

% TODO: maybe I can rephrase this into a stronger result specifically about
% a /\ ~p. Do I even want to do that?
\begin{lemma}
  Let $(p)$ be a principal ideal. For any $a, b \in \mathbf{B}$, $a/(p) \le
  b/(p)$ if and only if there exist $a', b' \in \mathbf{B}$ such that $a'/(p) =
  a/(p)$, $b'/(p) = b/(p)$, and $a' \le b'$.
\end{lemma}
\begin{proof}
  Let us begin with the `only of' direction, and let $f\colon \mathbf{B} \to
  \mathbf{B}/(p)$ be defined as $f(x) = x/(p)$. If $a' \le b'$, then $f(a') \le
  f(b')$ by \cref{lemma:canonical_homomorphism,lemma:homomorphisms_and_order}.
  Thus $a'/(p) \le b'/(p)$, and $a/(p) \le b/(p)$ as required.

  For the other direction, let $a, b \in \mathbf{B}$ be such that $a/(p) \le
  b/(p)$. Then, by \cref{lemma:order},
  \[
    [a/(p)] \land \neg [b/(p)] = (a \land \neg b)/(p) = 0/(p),
  \]
  i.e.,
  \[
    a \land \neg b \in (p) \quad \iff \quad a \land \neg b \le p \quad \iff
    \quad a \land \neg b \land \neg p = 0
  \]
  by \cref{def:ideal,lemma:order}. Let us pick $a' = a \land \neg p$ and $b' = b
  \land \neg p$ since they satisfy $a'/(p) = a/(p)$ and $b'/(p) = b/(p)$ by
  \cref{lemma:elements_in_quotients}. It remains to show that $a \land \neg p
  \le b \land \neg p$. By \cref{lemma:order}, this is equivalent to $a \land
  \neg p \land \neg(b \land \neg p) = 0$. But
  \[
    a \land \neg p \land \neg(b \land \neg p) = a \land \neg p \land (\neg b
    \lor p) = (a \land \neg p \land \neg b) \lor (a \land \neg p \land p) = a
    \land \neg p \land \neg b,
  \]
  and we already have that $a \land \neg p \land \neg b = 0$ by assumption.
\end{proof}

\begin{corollary}
  Let $I \subseteq \mathbf{B}$ be an ideal. If $\mathbf{B}$ is atomic, then so
  is $\mathbf{B}/I$.
\end{corollary}

\begin{lemma}
  Let $(p)$ be a principal ideal. For any $a \in \mathbf{B}$, if $a/(p)$ is an
  atom in $\mathbf{B}/(p)$, then $a \land \neg p$ is an atom in $\mathbf{B}$
  such that $(a \land \neg p)/I = a/I$, and $m^*(a/(p)) = m(a \land \neg p)$.
\end{lemma}

\begin{theorem}[Using the previous three results]
  Let $L \subset \mathbf{B}$ and $w\colon L \to \mathbb{R}_{\ge 0}$ be such that
  $\WMC_w\colon \mathbf{B} \to \mathbb{R}_{\ge0}$ is a WMC measure. Let $p \in
  \mathbf{B}$ be such that $\WMC(p) = 0$, and let $g\colon \mathbf{B}/(p) \to
  \mathbf{B}$ be defined as $g(a/(p)) = a \land \neg p$. Then $\WMC \circ g$
  is a WMC measure on $\mathbf{B}/(p)$ with respect to the same $L$ and $w$
  such that
  \[
    \begin{tikzcd}
      \mathbf{B} \arrow{d}[swap]{\WMC} & \mathbf{B}/(p) \arrow{l}[swap]{g}
      \arrow{dl}{\WMC \circ g} \\
      \mathbb{R}_{\ge 0}
    \end{tikzcd}
  \]
  commutes.
\end{theorem}

% TODO: how can WMC compute something in the quotient algebra?
% 1) The highlighted lemma from my notes.
% 2) the results about <=
% TODO: prove that the two ways to compute the probability give the same answer,
% i.e., how B(Delta) = B(L)/(not Delta).
% TODO: need an example of how we can compute probabilities in the quotient
% algebra.
% TODO: we can then move through the quotient BA using representatives we get
% from mapping true things to 1 and false things to 0.
